\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}   % Page margins to 1 inch
\usepackage{siunitx}
\NewDocumentCommand\Pounds{o}{%
\pounds\IfNoValueTF{#1}%
{\relax}{\,\num[round-precision=2,round-mode=places]{#1}}}
% Define a new command for formatting dollar amounts
\NewDocumentCommand\Dollars{o}{%
  \$\IfNoValueTF{#1}%
    {\relax}{\,\num[round-precision=2, round-mode=places]{#1}}}

\begin{document}
\section{Formatting}
\begin{enumerate}
    \item Rework header \& footer to include the chapter title and be less busy.
    \item Standardize capitalization for figures.
    \item Footnotes are being pulled into the list of figures, seen on fig. 7.2.
    \item Remove the extra large margin created by chapter*'s
    \item Remove the extra page created by the list of x's (especially the list of tables)
    \item Kerning all around seems a little off.
    \item The \texttt{IR array} is sometimes refered to as \texttt{IR Array} --- fix that.
    \item Normalize the flowchart's style (ex. the arrows are different types).
    \item Include robust intro and outro paragraphs to each chapter for better flow
    \item Bottom-justify the footnote for the color matching algorithm figure.
    \item omni should be possibly shown as ``Omni'' in the glossary.
    \item For `Integration II', use roman numerals so the II's connect at the top.
    \item Draw dimensions on the robot with reference rulers
    \item Fix dollar sign's to have the little space between then. I.E. \$14 vs \Dollars[14].
    \item Remove mentions of ``we'', seen in System Test \& Verification.
    \item In System Test \& Verification, when `test' is referenced, use a cref to the actual test.
    \item Standardize labeling of sections and figures and such.
        \quad \\ Ex. some are CamelCase, some are some-case, etc.
    \item Remove mentions of `this system'
        \quad \\ Ex. Seen in System Analysis \& System Performance Metrics beginning paragraph
    \item Recreate the greyline environment
        \begin{itemize}
            \item In some circumstances it creates a much larger margin on the top and bottom that needed to be rectified elsewhere
        \end{itemize}
    \item Remove the ``overfull hbox'' warnings
    \item 3\textsuperscript{rd} bibliography entry has really bad kerning.
    \item Bibliography formatting
    \item middleColor sensor graph should be larger
    \item Find a way to automatically make a figure fill up the rest of the space on the page.
        \quad \\ For example, middleColor sensor has missing space beneath it.
    \item Change the naming from middleColor \& leftColor etc. to Middle color, Left color, etc. on the calibraiton graphs
    \item Determine if periods are wanted after figure titles or not
    \item Determine if capitalized references are wanted. For example, do you say figure X in a sentence of Figure X?
\end{enumerate}
\section{Content}
\begin{enumerate}
    \item Add a listing of all the components used.
    \item Obstacle Avoidance flowchart.
    \item Remove mentions of design 1 \& design 2 in the Project Management plan --- they don't refer to the designs seen in the appendix.
    \item Include more photos of the construction, like the gearbox being taken apart, photos of the robot on the course itself, and a 3/4ths view
    \item Include an in-depth explanation of the IR array algorithm and error computation. 
    \item Mention the IR-array's moving average
    \item Include descriptions next to the flowchart to aid understanding
    \item Include robust intro and outro paragraphs to each chapter for better flow
    \item Get the timing info of other teams from the TA's
    \item Explain how the motor controller calibration happened \& what benefits it gives
    \item Remove dollar cost from detailed design
    \item Determine the reasoning for the missing checkmarks in System Test and Verification
    \item Add a link to the videos of the robot working
    \item Include the 3D printed files in the \LaTeX \ directory
    \item Add the obstacle avoidance course to the appendix
\end{enumerate}

\section{Code}
\subsection{Formatting}
\begin{enumerate}
    \item Update code margins to avoid spilling over into the next line.
    \item Add more code coloring, like \textless \ include \textgreater's and such.
    \item Add a full documentation history for each file
    \item Re-comment many of the files, especially \texttt{ObstacleAvoidance.h}
    \item Color A3, A4, A5, A6, A7, A8, \& A9 to black. Currently being colored as green as they are considered to be numbers.
    \item Possibly reduce font size for better comments
    \item Determine unused variables and remove them
    \item Place Utils somewhere else as it's small. Possibly figure out the actual way arduino should shut off.
    \item Rename CenterOnLine and CenterLine, as they do very different things.
\end{enumerate}

\subsection{Logic}
\begin{enumerate}
    \item Use header files for their true purpose instead of housing all code inside of them
    \item Convert all PWM based motor control commands to percentage of total speed commands
    \item Load in color calibration points from a json or something of the like.
    \item combine move functions so instead of movePercent and move, is an optional parameter
\end{enumerate}

\newpage
\section{Nice to have's}
\begin{enumerate}
    \item Replace all hand-drawn designs with \LaTeX \ figures
    \item Include a clickable link back to the table of contents for the header \& footer
    \item Rework the risk management section to provide lower risks as they are over-inflated.
    \item A more understandable motor calibration graph
    \item Color code the circuit diagram
\end{enumerate}

\end{document}