\documentclass[11pt]{report}
\usepackage{StyleSheets/main}
\begin{document}

\chapter{Summary}\label{ch:summary}
The goal for this project was to produce an autonomous vehicle which can accomplish two tasks: The robot needs to be able to avoid obstacles given a course to follow. The robot needs to pickup a box from a platform and follow a specific line to carry the box to a placement point. The process for the construction, testing, and designing of this vehicle were detailed in this report. 
\par This vehicle was created using different mechanical, electrical, and computer engineering related parts, methods, and ways of thinking. The plan for how this project was run and how the procedures took place was documented over the 10 weeks in \cref{ch:project-management-plan}. The requirements for this system were listed in \cref{ch:system-requirements}, and this section details the requirements needed to complete the two tasks. In this report, the details for how a user will initialize this system, maintain the robot, and shutdown the system were detailed in the \cref{ch:conops}. Different conceptual designs were discussed, located in \cref{ch:conceptual-design}, and the design methods on how the best design was chosen were detailed. The possible risks for this system were detailed in \cref{ch:system-risk-management}, which include damage to electrical parts or the lack of budget. A detailed design review of this vehicle was given in \cref{ch:detailed-design}, and the overall structure, wiring, and programming of this vehicle was deeply discussed. Lastly, the methods for how the vehicle was tested were discussed and the systems performance metrics were finalized in \cref{ch:system-test}. 

\par Within this project, the engineering design process was used. The overall goals set out for the project were completed and the system worked better than what was expected. The robot was dynamic, robust, and incredibly fast, leading it to meet and exceeded all of its performance metrics. Overall the project was deemed a success. 
\end{document}